\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{cite}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{\textrm{B \kern -.05em \textsc{i \kern -.025em b} \kern -.08em
T \kern -.1667em \lower .7ex \hbox{E} \kern -.125emX}}
\begin{document}

\title{Helix Requirements Management\\

}

\input{chapters/authors}

\maketitle

\begin{abstract}
Requirements management ensures that stakeholder objectives are consistent with the project's final results.
HelixRM offers a comprehensive solution for tracking, evaluating, deconstructing, and prioritizing requirements.
This paper investigates how HelixRM enhances collaboration, traceability, and adaptability in requirements management while integrating with widely utilized development tools.
\end{abstract}

\begin{IEEEkeywords}
Requirements Management, HelixRM, Traceability, Collaboration, Project Development
\end{IEEEkeywords}

\section{Introduction}\label{sec:introduction}
Requirements management is an essential aspect of effective project development, as it guarantees that stakeholder needs and objectives are clearly articulated, recorded, and tracked during the project lifecycle.
Proper requirements management minimizes the risk of scope creep, misunderstandings, and unmet goals, all of which can greatly affect project success.

HelixRM supports this process by providing a centralized platform for managing and decomposing requirements into actionable specifications.
With features like hierarchical organization, traceability, version control, and integration with tools such as Jira, HelixRM improves collaboration among stakeholders and guarantees that requirements align with business objectives.
Its functionalities empower teams to quickly respond to changes, maintain consistency, and enhance project transparency, making it an invaluable tool for overseeing complex or large-scale projects.

\section{Functionalities of HelixRM}\label{sec:functionalities-of-helixrm}

\input{chapters/track-requirements}
\input{chapters/review-requirements}
\input{chapters/decompose-requirements}
\input{chapters/prioritize-requirements}
\input{chapters/jira-integration}
\section{Advantages of HelixRM}\label{sec:advantages-of-helixrm}
\input{chapters/advantages}

\section{Limitations of HelixRM}\label{sec:limitations-of-helixrm}
\input{chapters/limitations}


\section{Acknowledgment}\label{sec:acknowledgment}
The preferred spelling of the word ``acknowledgment'' in America is without
an ``e'' after the ``g''.
Avoid the stilted expression ``one of us (R. B\@.
G.) thanks $\ldots$''.
Instead, try ``R. B. G. thanks$\ldots$''.
Put sponsor acknowledgments in the unnumbered footnote on the first page.

\section*{References}

Please number citations consecutively within brackets~\cite{b1}.
The sentence punctuation follows the bracket~\cite{b2}.
Refer simply to the reference number, as in~\cite{b3}---do not use ``Ref~\cite{b3}.'' or ``reference~\cite{b3}'' except at
the beginning of a sentence: ``Reference~\cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts.
Place the actual footnote at the bottom of the column in which it was cited.
Do not put footnotes in the abstract or reference list.
Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use
``et al.''.
Papers that have not been published, even if they have been
submitted for publication, should be cited as ``unpublished''~\cite{b4}.
Papers that have been accepted for publication should be cited as ``in press''~\cite{b5}.
Capitalize only the first word in a paper title, except for proper nouns and
element symbols.

For papers published in translation journals, please give the English
citation first, followed by the original foreign-language citation~\cite{b6}.


%\input{chapters/references-old}
\bibliographystyle{plain}
\bibliography{chapters/references}

\end{document}
